---
title: "p8105_hw6_gl2761"
author: "Gonghao Liu"
date: "12/3/2022"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(purrr)
library(patchwork)
library(broom)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

### Loading data
```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

## Problem 2

### Read in and clean data

```{r}
homicide_df =
  read.csv("./data_WP/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, ', ', state),
    resolved = case_when(
           disposition =="Closed without arrest" ~ 0,
           disposition =="Open/No arrest" ~ 0,
           disposition =="Closed by arrest" ~ 1
         )) %>% 
  subset(city_state!="Dallas, TX" & city_state!="Phoenix, AZ" & city_state!="Kansas City, MO" & city_state!="Tulsa, AL") %>%
  filter(victim_race == "White" | victim_race == "Black") %>%
  relocate(city_state)
```

### Analysis for Baltimore

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

baltimore_fit = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

baltimore_fit %>% 
  broom::tidy(conf.int = T) %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(exp(conf.low)),
         CI_upper = exp(exp(conf.high)),
         p_val = rstatix::p_format(p.value, digits = 2)) %>% 
  select(term, OR, CI_lower,CI_upper, p_val) %>% 
  knitr::kable(digits = 3, align = "lccc", 
               col.names = c("Term", "Estimated adjusted OR", "CI lower bound", "CI upper bound", "p-value"))
```

For the city of Baltimore, MD, controlling for all other variables, for homicides cases whose victim is male are significantly less like to be resolved than those whose victim is female.

### Analysis for all cities

```{r}
cities_fit = homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial(link = "logit"))),
    results = map(models, ~broom::tidy(.x, conf.int = T))) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(conf.low),
    CI_upper = exp(conf.high),
    p_val = rstatix::p_format(p.value, digits = 2)
  ) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, OR, CI_lower,CI_upper, p_val) 

cities_fit %>% 
  knitr::kable(digits = 3, align = "llccc", col.names = c("City", "Estimated adjusted OR", "CI lower bound", "CI upper bound", "p-value"))
```

```{r}
cities_fit %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(x = "City", y = "Estimated OR with CI")
```

For most of the cities, the estimated odds ratio is less than 1, and about half of cities have CI that doesn't contain 1, which means for most of the cities, controlling for all other variables, for homicides cases whose victim is male are significantly less like to be resolved than those whose victim is female.

## Problem 3

### Load and clean the data for regression analysis.
```{r}
birthweight_df = read.csv("./birthweight.csv") %>% 
  janitor::clean_names()

# Check missing value
sum(is.na(birthweight_df))

birthweight_df = birthweight_df %>% 
  mutate(
    babysex = factor(babysex, ordered = FALSE),
    frace = factor(frace, ordered = FALSE),
    malform = factor(malform, ordered = FALSE),
    mrace = factor(mrace, ordered = FALSE)
  )
```

### Propose a regression model for birthweight.

```{r}
model_1 = lm(bwt ~ ppbmi + delwt + gaweeks + momage + smoken + wtgain, data = birthweight_df) 

model_1 %>% broom::tidy()

plot = birthweight_df %>% 
  add_residuals(model_1) %>% 
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_abline(slope = 0, intercept = 0, color = "red") +
  labs(
    title = "Residuals vs Fitted value Plot",
    x = "Fitted value",
    y = "Residuals"
  ) +
  theme(plot.title = element_text(hjust = 0.5))

plot

```

Describe modeling process:

1. Firstly, load and clean data;

2. Then I think "mother's weight at delivery (pounds)", 'gestational age in weeks', 'mother’s age at delivery', 'average number of cigarettes smoked per day during pregnancy', 'mother’s weight gain during pregnancy (pounds)' and "mother's pre-pregnancy BMI" may influence baby's birth weight, so I use these two variables as the predictors of the model;

3. Then I drew a "Residuals vs Fitted value Plot". From the plot, residual values are bounce around 0, which means they are evenly distributed around 0. Therefore, it is a reasonable model and I keep this model.


### Compare my model to two others:

```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_df)

cv_df = crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    mod_1 = map(.x = train, ~lm(bwt ~ ppbmi + delwt, data = .x)),
    mod_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = mod_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = mod_3, .y = test, ~rmse(model = .x, data = .y))) %>%
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) 

cv_df %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(title = "RMSEs for Each Model",
       x = "Model",
       y = "RMSE") +
  theme(plot.title = element_text(hjust = 0.5))
```

Based on the violin plot, we can find that model 1 has a higher error rate than the other two models and model 3 has the smallest RMSE value. Model 3 is more accurate than model 1 and model 2.