---
title: "p8105_hw6_gl2761"
author: "Gonghao Liu"
date: "12/3/2022"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(purrr)
library(patchwork)
library(broom)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

### Loading data
```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

## Problem 2

### Read in and clean data

```{r}
homicide_df =
  read.csv("./data_WP/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, ', ', state),
    resolved = case_when(
           disposition =="Closed without arrest" ~ 0,
           disposition =="Open/No arrest" ~ 0,
           disposition =="Closed by arrest" ~ 1
         )) %>% 
  subset(city_state!="Dallas, TX" & city_state!="Phoenix, AZ" & city_state!="Kansas City, MO" & city_state!="Tulsa, AL") %>%
  filter(victim_race == "White" | victim_race == "Black") %>%
  relocate(city_state)
```

### Analysis for Baltimore

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

baltimore_fit = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

baltimore_fit %>%
  broom::tidy() %>%
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) 
```

## Problem 3

### Load and clean the data for regression analysis.
```{r}
birthweight_df = read.csv("./birthweight.csv") %>% 
  janitor::clean_names()

# Check missing value
sum(is.na(birthweight_df))

birthweight_df = birthweight_df %>% 
  mutate(
    babysex = factor(babysex, ordered = FALSE),
    frace = factor(frace, ordered = FALSE),
    malform = factor(malform, ordered = FALSE),
    mrace = factor(mrace, ordered = FALSE)
  )
```

### Propose a regression model for birthweight.

```{r}
model_1 = lm(bwt ~ ppbmi + delwt, data = birthweight_df) 

model_1 %>% broom::tidy()

plot = birthweight_df %>% 
  add_residuals(model_1) %>% 
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_abline(slope = 0, intercept = 0, color = "red") +
  labs(
    title = "Residuals vs Fitted value Plot",
    x = "Fitted value",
    y = "Residuals"
  ) +
  theme(plot.title = element_text(hjust = 0.5))

```

Describe modeling process:
1. Firstly, load and clean data;
2. Then I think "mother's weight at delivery (pounds)" and "mother's pre-pregnancy BMI" my influence baby's birth weight, so I use these two variables as the predictors of the model;
3. Then I drew a "Residuals vs Fitted value Plot". From the plot, residual values are bounce around 0, which means they are evenly distributed around 0. Therefore, it is a reasonable model and I keep this model.


#### Compare your model to two others:
```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_df)

cv_df = crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    mod_1 = map(.x = train, ~lm(bwt ~ ppbmi + delwt, data = .x)),
    mod_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = mod_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = mod_3, .y = test, ~rmse(model = .x, data = .y))) %>%
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(title = "RMSEs for Each Model",
       x = "Model",
       y = "RMSE") +
  theme(plot.title = element_text(hjust = 0.5))
```

Based on the violin plot, we can find that model 1 has a higher error rate than the other two models and model 3 has the smallest RMSE value. Model 3 is more accurate than model 1 and model 2.